\documentclass{article}
\input{setup.tex}


\renewcommand*\contentsname{Table of Content}

\title{Complex Function Theory}
\author{Mattie Ji}
\date{Fall 2022}
\setlength\parindent{0pt}

\begin{document}

\maketitle
These are lecture notes from \textbf{MATH 2250: Complex Function Theory} with Professor Sergei Treil at Brown University for the Fall 2022 semester, with some supplemental materials written by the note-taker herself. The most up-to-date version of the notes are maintained in the note \href{https://github.com/maroon-scorch/MATH2550-notes}{repository}.\\

These notes are taken by \href{https://github.com/maroon-scorch}{Mattie Ji} with gracious help and input from the instructor of this course. If you find any mistakes in these notes, please feel free to direct them via email to me or send a pull request on GitHub.\\

The notes are last updated \today.
\tableofcontents
\newpage

\include{Lecture/lecture-1.tex}
\include{Lecture/lecture-2.tex}
\include{Lecture/lecture-3.tex}
\include{Lecture/lecture-4.tex}
\include{Lecture/lecture-5.tex}
\include{Lecture/lecture-6.tex}
\include{Lecture/lecture-7.tex}
\include{Lecture/lecture-8.tex}
\include{Lecture/lecture-9.tex}
\include{Lecture/lecture-10.tex}
\include{Lecture/lecture-11.tex}
\include{Lecture/lecture-12.tex}
\include{Lecture/lecture-13.tex}
\include{Lecture/lecture-14.tex}

% \section{Lecture 15 - 10/12/2022}

% \subsection{Jump Theorem for Cauchy Integrals}
% Let $\gamma \in PC^1$ with image $\Gamma := \gamma([a, b]) \subset \Cbb$, and let $f(z)$ be a continuous function on $\Gamma$.

% \begin{definition}
% The \textbf{Cauchy Integral} of $f(z)$ along $\gamma$ is the function
% \[F(\xi) \coloneqq \frac{1}{2\pi i} \int_\gamma \frac{f(z)}{z - \xi} dz, \forall \xi \in \Cbb \setminus \Gamma\]
% Note that as we take $\xi$ to infinity, $F(\xi) = 0$. Furthermore, $F(\xi)$ is analytic on $\Cbb \setminus \Gamma$ since it could be represented in power series by geometric expansion.
% \end{definition}

% \begin{example}
% If $\gamma$ is a closed loop and $f(z)$ is identically $1$, then the Cauchy integral of $f(z)$ around $\gamma$ is exactly the winding number $F(\xi) = w(\gamma, \xi)$ of $\gamma$ around $\xi$, which is either $1$ if the point is inside or $0$ if the point is outside.
% \end{example}

% \begin{theorem}[Plemelj-Sokhotsky Theorem]
% Let $\gamma$ 
% \end{theorem}

\section{Lecture - 10/31/2022}

\subsection{Runge's Theorem}

In this lecture, we will prove Runge's Theorem. (Fun Fact: The Runge–Kutta methods in Numerical Analysis comes from the same mathematician Carl Runge)

\begin{theorem}[Runge's Theorem]
    Let $K$ be compact, $f \in Hol(K)$ (recall this means that there exists some open $\Omega$ containing $K$ where $f \in Hol(\Omega)$), then
    \begin{enumerate}
        \item There exist a sequence of rational functions $\{f_n\}_{n = 1}^\infty$ with poles NOT in $K$ such that $\{f_n\}$ converges to $f$ uniformly on $K$
        \item Let $\{\mathcal{O}_k\}$ be connected components of $\Cbb \setminus K$ (Note that the collection $\{\mathcal{O}_k\}$ is countable by separability and denseness of $\Rbb^2$), fix $z_k \in \mathcal{O}_k$ for each k, then one can choose the rational $\{f_n\}_{n = 1}^\infty$ as before such that they only have poles at $z_k$.
    \end{enumerate}
\end{theorem}

\begin{proof}
    We will first prove $(1)$:\\\\
    \[\noindent\fbox{%
    \parbox{\textwidth}{%
    \underline{Idea: } The idea is to find some bounded open $G$ with $\partial G \in PC^1$ such that
    \[K \subseteq G \subseteq cl(G) \subsetq \Omega\]
    Then using Cauchy's Integral Formula:
    \[f(z) = \frac{1}{2\pi i} \int_{\partial G} \frac{f(\xi)}{\xi - z} d\xi\]
    We can actually approximate the integral using Riemann Sums to get
    \[f(z) \sim \sum \frac{f(\xi_k)}{\xi_k - z} (\xi_k - \xi_{k-1})\]
    , which would be get us a rational approximation, but showing the uniform convergence is a bit tedious. We will however generalize this idea topologically, as shown below.
    }%
}\]
   Let $\gamma = \partial G$, we want to divide $\gamma$ into finitely many non-overlapping (intersect at most at vertices) arcs $\{\gamma_k\}$ such that each $\gamma_k$ is contained in $D_{\lambda_k, \delta_k}$ such that $D_{\lambda_k, 2 \delta_k} \subseteq \Cbb \setminus K$. There are two ways to find the $\delta$ we want: 
\begin{enumerate}
    \item In practice, recall we usually construct our desired $G$ using rectangular grids, so its boundary is just some straight-lines. Then, fix $\delta < dist(\gamma, K)/2$, then we can split each interval to be less than $\delta$
    \item Using some abuse of notation, write $\gamma: [a, b] \\to \Omega$, then we can cover the image of $\gamma$ by open disks $D_{z, \delta}$ using the Lebesgue Number Lemma, which will also give our desired result.
\end{enumerate}
Now, using the arcs $\{\gamma_k\}$, we have that
\[\frac{1}{2\pi i} \int_\gamma \frac{f(\xi)}{\xi - z} d\xi = \sum_{1}^N \frac{1}{2\pi i} \int_{\gamma_k} \frac{f(\xi)}{\xi - z} dz\]
, where for simplicity we will write $\varphi_k(z) = \frac{1}{2\pi i} \int_{\gamma_k} \frac{f(\xi)}{\xi - z} dz$, so we have that
\[f(z) = \sum_1^N \varphi_k(z)\]
Note that $\varphi_k(z)$ is analytic for $|z - \lambda_k| > \varphi_k$ and furthermore that $\varphi_k(z) \to 0$ as $z \to \infty$. Thus, we can write each $\varphi_k(z)$ as the Laurent Series
\[\varphi_k(z) = \sum_{j \geq 1} a_j^k (z - \lambda_k)^{-j}\]
, which converges uniformly on compact subsets on $(D_{\lambda_k, \delta_k})^c$, and hence on $K$.\\\\
Now take $\epsilon > 0$, we can approximate each $\varphi_k$ by finite sum
\[\sum_{j = 1}^{N_k} a^k_j (z - \lambda_k)^{-j}\]
, up to $\epsilon/N$. Hence we have that
\begin{align*}
    |f(z) - \sum_{k = 1}^N \sum_{j = 1}^{N_k} a_j^k (z - \lambda_k)^{-j}| < \epsilon
\end{align*}
The inner function $\sum_{k = 1}^N \sum_{j = 1}^{N_k} a_j^k (z - \lambda_k)^{-j}|$ is rational, he nce we have a rational approximation that converges uniformly. This concludes the proof of $(1)$.\\\\
We will now proce $(2)$:
    \[\noindent\fbox{%
    \parbox{\textwidth}{%
    \underline{Idea: } Consider $z_k, \lambda \in \mathcal{O}_k$, ie. that they belong in the same connected component. Let $f$ be some rational function with pole at $z_k$, then our goal is to show that there's a rational approximation of $f$ with poles on $\lambda$, using a continuous induction.
    }%
}\]
We will first introduce a short lemma:
\begin{lemma}
    Let $\mathcal{O}$ be open and connected, let $K$ be a compact subset of $\Cbb \setminus \mathcal{O}$. Suppose $a \in \mathcal{O}$, $\lambda \in \Cbb$ such that
    \[|a - \lambda| < dist(a, \Cbb \setminus \mathcal{O})\]
    , then any rational (resp. proper rational) function with pole at $\lambda$ can be approximated by rational (resp. proper rational) functions uniformly with pole at $a$.
\end{lemma}

\begin{proof}[Proof of Lemma]
    The proof for proper rational function follows similarly to the case of rational functions. Let $\delta$ be some number between
    \[|a - \lambda| < \delta < dist(a, \Cbb \setminus \mathcal{O})\]
    , and suppose $f$ is a rational function with pole at $\lambda$.\\\\
    In particular, $f$ is analytic at $z: |z - a| > \delta$, hence $f$ can be written as
    \[\sum_{k \in \Zbb} a_k (z - a)^k\]
    , which converges uniformly on compact subsets of $\{z: |z - a| > \delta\}$. Since $K$ is a compact subset of $\{z: |z - a| > \delta\}$, we have a uniform convergence on $K$.
    \end{proof}
Now back to our setup, let $z_k \in \mathcal{O}_k$. Define
\[A \coloneqq \{\lambda \in \mathcal{O}_k | \text{ any rational function with pole at $\lambda$ can be approximated by functions with poles at $z_k$}\}\]
Clearly $z_k \in A$. Now, we claim $A$ is open. Indeed, for any $a \in A$, we know there exist $\delta > 0$, such that for all $|\lambda - a| < \delta$, any rational function with pole at $\lambda$ can be approximated by finite sum $\sum \frac{c_k}{(z - a)^k}$. Then we know that
\[|f_{\text{pole at $\lambda$}} - f_{\text{pole at $a$}}| < \frac{\epsilon}{2}\ \text{, by Lemma}\]
\[|f_{\text{pole at $z_k$}} - f_{\text{pole at $a$}}| < \frac{\epsilon}{2}\ \text{, by Definition of A}\]
Hence, 
\[|f_{\text{pole at $z_k$}} - f_{\text{pole at $\lambda$}}| < \epsilon\]
Now we claim that $A$ is also closed. Indeed, let $\lambda \notin A$ and take $\delta < \frac{dist(\lambda, \mathcal{O}^c}){4}$, then for all $a$ such that $|a - \lambda| < \delta$, $D_{a, \delta} \subseteq \mathcal{O}_k$. Now suppose for contradiction that $a \in A$, then our Lemma implies that $\lambda \in A$, which is false. Hence $a \notin A$. Thus, $A$ is closed.\\\\
Since $\mathcal{O}_k$ is connected and $A$ is a non-empty clopen subset of $\mathcal{O}_k$, we have that $A = \mathcal{O}_k$.
\end{proof}

\begin{remark}
    Note that a nearly identical argument shows that Runge's Theorem holds for proper rational functions too.
\end{remark}



\end{document}
